Filtering figure

### 2020-05-05 main_figures/filtering.Rmd
reduced dots size and opacity to make overlaps more visible

@@

p2 <- ggplot(m, aes(maxPCout, F1atK, group=method, colour=filter, shape=doubletRemoval)) + geom_point(size=3) +
  # geom_line(aes(group=doubletRemoval), colour="lightgrey") + 
  facet_wrap(~dataset, scales="free") + scale_color_manual(values=cols) + 
  xlab("Maximum proportion of cells excluded per subpopulation") + ylab("mean F1 at true number of clusters")

>>>>

```{r, include=FALSE}
# requires old pipeComp version
devtools::load_all("pipeComp_biorxiv/pipeComp/")
```

@@

p2 <- ggplot(m, aes(maxPCout, F1atK, group=method, colour=filter, shape=doubletRemoval)) + geom_point(size=2.2,alpha=0.8) +
  # geom_line(aes(group=doubletRemoval), colour="lightgrey") + 
  facet_wrap(~dataset, scales="free") + scale_color_manual(values=cols) + 
  xlab("Maximum proportion of cells excluded per subpopulation") + ylab("mean F1 at true number of clusters")
